Fig1

### 2020-03-06 analysis/figure-1.Rmd
new fig 1
now with tsne fig 5

subsetmaketsne <- function(whichtissue, whichtreatment, whichsex){

  colData <- colData %>%
    dplyr::filter(tissue %in% whichtissue,
                  treatment %in% whichtreatment,
                  sex %in% whichsex) 
  row.names(colData) <- colData$V1

  # save counts that match colData
  savecols <- as.character(colData$V1) 
  savecols <- as.vector(savecols)

  countData <- as.data.frame(t(countData))
  countData <- countData %>% dplyr::select(one_of(savecols)) 
  countData <- as.data.frame(t(countData))

  euclidist <- dist(countData) # euclidean distances between the rows

  tsne_model <- Rtsne(euclidist, check_duplicates=FALSE, pca=TRUE, perplexity=10, theta=0.5, dims=2)
  tsne_df = as.data.frame(tsne_model$Y)

  # prep for adding columns
  colData2 <- colData 
  colData2$V1 <- NULL
  tsne_df_cols <- cbind(colData2, tsne_df)
  return(tsne_df_cols)
}

@@

plottsneelipse <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 1, aes(color = tissue )) 
  return(p)
}

@@

plottsneelipsev2 <- function(tsnedf, pointcolor, whichcolors){
  p <- ggplot(tsnedf, aes(x = V1, y = V2)) +
    geom_point(size = 1, aes(color = pointcolor)) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank()) +
    stat_ellipse(linetype = 1, aes(color = treatment)) 
  return(p)
}

@@

>>>>

@@

@@

@@

```{r}
write.csv(chartsne, "../../musicalgenes/data/tsne.csv")
```
